### 2019-07-29 introduction.tex
Started TTV section. Added section This work

In Figure~\ref{transit} is described the architecture of a transiting exoplanet. When the planet passes in front of its star produced a dimming in its flux called primary transit. The maximum drop during the transit event defines the transit depth $\Delta{F}$:

@@

@@

>>>>

In Figure~\ref{transit} is described the architecture of a transiting exoplanet. Thanks to its geometry, the transit event as well as some parameters of the planetary system can be described with a few simple relations (cite Seager and Mallean y Winn).  When the planet passes in front of its star produced a dimming in its flux called primary transit. The maximum drop during the transit event defines the transit depth $\Delta{F}$:

@@

TO DO: Add studies about transmission spectroscopy.

@@

Since the discovery of the first exoplanet, one of the principal questions that arose was: are they alone in their systems? The idea of multiplanetary system is a consequence of our knowlegde about the planetary system where we live in, and until today the Solar System has the larger number of orbiting planets. Besides the Solar System, Kepler-90 has the same number of confirmed exoplanets: eight. Statistically, around a 20\% of the confirmed exoplanets live in a multiplanetary system, but this number is theoretically larger (cite).

The Transit Timing Variations technique was proposed as a way to detect Earth-mass planet in multiplanetary systems due to gravitational interactions \citep{Holman2005,Agol2005}. A planet in a Keplerian orbit will transit its star following a linear function of the orbital period, but the presence of a second planet could produce transits no exactly periodic.

\section{This work}
